%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemTwo}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}%\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingOne}[2]{
  \vspace{-1pt}%\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingTwo}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    %   \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemTwo}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{}%\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{}%\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% %----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://daisy91530.github.io/}{\Huge Tieh (Daisy) Chu}}\\\\
% %   \vspace{0.5em}
%   \color{blue}\href{https://www.linkedin.com/in/daisy-tieh-chu/}{linkedin.com/in/daisy-tieh-chu} & Email : \color{blue}\href{mailto:tiehchu2@illinois.edu}{tiehchu2@illinois.edu}\\
  
%   \color{blue}\href{https://daisy91530.github.io/}{https://daisy91530.github.io/} & Mobile : +886-983-234-938 \\
% \end{tabular*}

%----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{https://daisy91530.github.io/}{\Huge Tieh (Daisy) Chu}}\\
% %   \vspace{0.5em}

    
%         \color{blue}\href{mailto:tiehchu2@illinois.edu}{tiehchu2@illinois.edu}      \color{blue}\href{https://www.linkedin.com/in/daisy-tieh-chu/}{linkedin.com/in/daisy-tieh-chu}       \color{blue}\href{https://daisy91530.github.io/}{https://daisy91530.github.io/}\\
    
  
% \end{tabular*}
\begin{center}
    \textbf{{\Huge Chia-An Lee}}\\
    \vspace{0.5em}
    
    \color{black}(+886) 905-690-190
    \color{blue}\href{mailto:sz110010@gmail.com}{sz110010@gmail.com}\\
    % \color{black} $\diamond$
    \color{blue}\href{https://www.linkedin.com/in/calee0219/}{LinkedIn}\color{black}$,$ \color{blue}\href{https://github.com/calee0219}{GitHub}\color{black}$,$ \color{blue}\href{https://calee.xyz/}{calee.xyz}
    
\end{center}
\vspace{-1em}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Yang Ming Chiao Tung University}{Jun. 2019 -- Jul. 2021}
      {Master of Science in Computer Science}{Hsinchu, Taiwan}
      \resumeItemListStart
        \resumeItemTwo{Advisor: \href{https://people.cs.nctu.edu.tw/~jcc/}{Jyh-Cheng Chen} @ \href{http://wire.cs.nctu.edu.tw/}{Wireless Internet Research and Engineering Laboratory}}
        \resumeItemTwo{Research focuses on 5G core network}
      \resumeItemListEnd
    \resumeSubheading
      {National Chiao Tung University}{Sep. 2015 -- Jun. 2019}
      {Bachelor of Science in Computer Science}{Hsinchu, Taiwan}
    %   \resumeItemListStart
    %     \resumeItemTwo{Coursework: Parallel Programming, Network Programming, Computer Security, IoT, Computer Network}
    %     \resumeItemTwo{Dean's List Fall 2016, Fall 2017, Fall 2018, Spring 2019}
    %   \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Intern (BlockChain)}{Jul. 2017 -- Dec. 2017}
      {\href{https://www.nchc.org.tw/}{National Center for High-Performance Computing}}{Hsinchu, Taiwan}
      \resumeItemListStart
        % \resumeItemTwo{Contributed to {\bf 24+ slot games} on the game server {\bf (20k users per day)} and succeeded in handling game-related issues with cross-functional teams.}
        \resumeItemTwo{Maintaining a private chain inside NCHC's server and testing some applications on it.}
      \resumeItemListEnd
    \resumeSubheading
      {Intern (Container Platform)}{Jul. 2018 -- Dec. 2018}
      {\href{https://www.nchc.org.tw/}{National Center for High-Performance Computing}}{Hsinchu, Taiwan}
      \resumeItemListStart
        \resumeItemTwo{NCHC provides customers a GPU platform as a PaaS to run their ML model. To solve the resource dispatching problem in lightweight, we design a GPU computing platform prototype base on Docker containers.}
        \resumeItemTwo{The prototype has been invited to give a short talk at \href{https://cis.ncu.edu.tw/SeminarSys/activity/TANET2018/news/19}{TANET 2018}.}
        % \resumeItemTwo{Overhauled the system, which led to an average of {\bf 23\% improvement} on server response time by refining code, reducing database access time, and optimizing MySQL query performance.}
        % \resumeItemTwo{Drove a testing effort, getting test coverage from an estimate of {\bf 70\% to 80\%} and reducing bug tickets by {\bf 60\%}.}
      \resumeItemListEnd
    \resumeSubheading
      {Team Lead (Network Team)}{Feb. 2018 -- Sep. 2019}
      {\href{https://it.cs.nycu.edu.tw/}{National Chiao Tung University Computer Science Computer Center}}{Hsinchu, Taiwan}
      \resumeItemListStart
      \resumeItemTwo{Lead the network team to host all the networking of our department. Including service intra-net design and deployment, 3-layer internet architecture, static and dynamic routing, IPv6, network high availability, and VPN networking.}
      \resumeItemTwo{Lead our team to deploy alarming systems for network and service via \href{https://www.nagios.org/}{Nagious}, \href{https://www.cacti.net/}{Cacti}, and \href{https://www.librenms.org/}{LibreNMS}.}
      \resumeItemTwo{Host the co-location center for our department. Including once center rebuild and server migration.}
      \resumeItemListEnd
    \resumeSubheading
      {Part-Time (Linux Team, PC Team)}{Feb. 2018 -- Sep. 2019}
      {\href{https://it.cs.nycu.edu.tw/}{National Chiao Tung University Computer Science Computer Center}}{Hsinchu, Taiwan}
      \resumeItemListStart
      \resumeItemTwo{Managing Linux workstations. Routine jobs include package updating, LDAP usage, log watching, abnormal user behavior checking, etc.}
      \resumeItemTwo{Managing Windows PC. Deploy OS via Clonezilla and application via Ansible. Fix hardware issues.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
% \section{Honors \& Awards}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {ACM ICPC 2017 Asia Hua-Lien Regional Contest}{Sep. 2017}
%       {Silver Medal}{Hua-Lien, Taiwan}
%     \resumeSubheading
%       {ACM ICPC 2017 Asia Jakarta Regional Contest}{Nov. 2017}
%       {Honorable Mention}{Jakarta, Indonesia}
%   \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Educational Project \& Awards}
  \resumeSubHeadingListStart
     \resumeSubheadingOne
     {Awards}{}
      \resumeItemListStart
        \resumeItemTwo{ACM ICPC 2017 Asia Hua-Lien Regional Contest, Sep. 2017}{Silver Medal}
        \resumeItemTwo{ACM ICPC 2017 Asia Jakarta Regional Contest, Nov. 2017}{Honorable Mention}
        \resumeItemTwo{National Collegiate Programming Contest}{$14^{th}$ Place}
      \resumeItemListEnd
    \resumeSubheading
     {Project \href{https://www.free5gc.org/}{free5GC}}{Jan. 2019 -- Jul. 2021}
      {An open-source 5G core network}{}
      \resumeItemListStart
        \resumeItemTwo{The free5GC is an open-source project for 5G core networks. We aim to be the first open-sources 5G core network to make experiments and developments on 5G core quicker and easier than before.}
        \resumeItemTwo{Mainly focus on the user plane function, UPF. Implement the N4 interface to receive rules from SMF and add them into user plane data forwarding process.}
        \resumeItemTwo{To improve the performance of this project, comes out with my thesis: \textbf{\textit{\href{https://hdl.handle.net/11296/44vnys}{Design and Implementation of a Low­Latency and High­Throughput 5G Core Network}}}. In this thesis, we port free5GC on to \href{http://sdnfv.github.io/onvm/}{OpenNetVM} platform, which is a platform focusing on using DPDK and shared memory to improve the performance of network processing.}
        \resumeItemTwo{In the thesis, it rich 11 times throughput in user plane and one half of latency in control plane communication.}
      \resumeItemListEnd
    \resumeSubheading
     {NCTU CSCC Intranet Infrastructure}{2018}
      {Intranet design and implementation}{}
      \resumeItemListStart
        \resumeItemTwo{In the path, CSCC exposed all the services in the public network with firewall protection. It is moss-grown architecture with a waste of public IP resources, non-flexible, hard to scale, and not secured.}
        \resumeItemTwo{Redesign and deploy the intranet infrastructure for CSCC's services. Including 2-layer network architecture, NAT, firewall, DMZ, HA, and others intranet design.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%--------PROGRAMMING SKILLS------------
\section{Skills}
    \begin{tabular}{ l l }
     \textbf{Programming Languages}\qquad \qquad \qquad & C/C++, Go, Python, Shell Script\\
     \textbf{Professional Skills} & Linux, CCNP equivalent, IPv6, VPN, firewall, 5G, Docker, OS, Git, \LaTeX\\
     \end{tabular}
\end{document}
